We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
edit

Figure \ref{fig:expected_number} summarizes the results from this
experiment. 
The left panel shows the probability density for the number of M31
systems in a parent sampe of $10^4$ pairs, the right panel shows the
results for the MW.

>>>>

Figure \ref{fig:expected_number} summarizes the results from this
experiment. 
The left panel shows the probability density for the number of M31
systems in a parent sampe of $10^4$ pairs, the right panel shows the
results for the MW.
For M31, between $37\%$ to $58\%$ of the pairs have a satellite
distribution as aspherical as M31 in observations; this fraction drops
dramatically for the MW where only $0.03\% to 2\%$ of the satellites
are expected to have extreme aspherical distributions as the MW.
Considering the joint distribution of M31 and MW we find that at most
$1\%$ of the pairs are expected to be similar to the LG.
